---
title: "TA Session Week 5"
author: "Kamya"
date: "2/7/2020"
output: html_document
---

```{r setup, include=FALSE}
install.packages("tidyverse")
library(tidyverse)  
knitr::opts_chunk$set(echo = TRUE)
```


Read the data
```{r cars}
mydata=read.csv("C://Users/kamya/Downloads/TA/TA Session Week 5/Paneldata.csv")
mydata
```

Dummy variable to indicate the time when the treatment started. 
Treatment starts in 1994. 
```{r}
mydata$time = ifelse(mydata$year >= 1994, 1, 0)
head(mydata)
```
Dummy variable for groups exposed to the treatment. A,B,C,D were nottreated and E,F,G were treated
```{r}
mydata$treated = ifelse(mydata$country == "E" |mydata$country == "F" |mydata$country == "G", 1, 0)
head(mydata)
```
METHOD 1

Create an interaction between time and treated, call it did. 
```{r}
mydata$did = mydata$time * mydata$treated
mydata
```

Estimating the DID estimator
```{r}
didreg = lm(y ~ treated + time + did, data = mydata)
summary(didreg)
didreg2 = lm(y ~ treated + time , data = mydata)
summary(didreg2)
```
METHOD 2

```{R}
# Compute the four data points needed in the DID calculation:
a = sapply(subset(mydata, time == 0 & treated == 0, select=y), mean)
b = sapply(subset(mydata, time == 0 & treated == 1, select=y), mean)
c = sapply(subset(mydata, time == 1 & treated == 0, select=y), mean)
d = sapply(subset(mydata, time == 1 & treated == 1, select=y), mean)
 
# Difference in difference parameter
(d-c)-(b-a)

```


```{R}

df <- df %>%
  mutate(pred_prob_Model4 = predict(Model4, newdata = ., type = "response")) 
%>% mutate(pred_outcome_Model4 = ifelse(pred_prob_Model4 >= 0.5, 1,0))
