---
title: "Week4_TA_Session"
author: "Ajinkya Panaskar"
date: "2/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}


```

```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(ISLR)
library(ROCR)
```


```{r}
GradesR <- read_csv("GradesR.csv")
```

Boxplot - Hours vs Grades

```{r}

# Used factor function to convert Grade to a categorical variable 

ggplot(data=GradesR, aes(x=factor(Grade), y = Hours, fill=factor(Grade))) + geom_boxplot() + ggtitle("BoxPlot for Hours of Studying vs. Grade") + labs(x="Grade", y="Hours")
```

Fitting linear model for Grade vs. Hours 

```{r}
ggplot(GradesR, aes(x=Hours, y=Grade)) + geom_point() +
  scale_colour_hue(l=50) + 
  geom_smooth(method=lm,   # Add linear regression lines
              se=FALSE,    # Don't add shaded confidence region
              fullrange=TRUE) 

```

```{r}
a.lm <- lm(formula = Grade ~ Hours, data = GradesR)
summary(a.lm)
anova(a.lm)

```

Comparing performance of linear model (Red) with Logistic regression model (Blue)
```{r}
ggplot(GradesR, aes(x=Hours, y=Grade)) + geom_point() + 
# add logit curve
  stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE) +
#add the regression line
    geom_smooth(method=lm,  color="red", # Add linear regression lines
              se=FALSE,    # Don't add shaded confidence region
              fullrange=TRUE) 
```

Default dataset: ISLR library

```{r}
Default_df <- Default
glimpse(Default_df)
```

```{r}
Default_df <- Default_df %>% mutate(dft_cat = ifelse(default=="Yes",1,0),
                      stdt_cat = ifelse(student=="Yes",1,0))
```

Logistic Model 1
```{r}
Model1 <- glm(dft_cat ~ 1 , data = Default_df, family = "binomial")
summary(Model1)

Default_df %>% group_by(default) %>% summarise(number_of_datapoints=n())
```

Logistic Model 2

```{r}
Model2 <- glm(dft_cat ~ stdt_cat , data = Default_df, family = "binomial")
summary(Model2)
```

Logistic Model 3

```{r}
Model3 <- glm(dft_cat ~ balance , data = Default_df, family = "binomial")
summary(Model3)

ggplot(Default_df, aes(x=balance, y=dft_cat)) + geom_point() + stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)

```
Logistic Model 4

```{r}
Model4 <- glm(dft_cat ~ balance + income + stdt_cat, data = Default_df, family = "binomial")
summary(Model4)
```

Predicting default using Model 4

```{r}
Default_df <- Default_df %>% 
  mutate(pred_prob_model4 = predict(Model4, newdata = ., type = "response")) %>% 
  mutate(pred_outcome_model4 = ifelse(pred_prob_model4 >= 0.5,1,0))
```

```{r}
ggplot(data=Default_df, aes(x=balance, y=pred_prob_model4, group=student, colour=student)) +
  geom_line() +
  geom_hline(aes(yintercept=0.058), colour="blue", linetype="dashed")+
  geom_hline(aes(yintercept=0.015), colour="#990000", linetype="dashed") + 
  labs(x="Balance", y="Default Rate") 
  
```

Confusion Matrix

```{r}
xtabs(~dft_cat + pred_outcome_model4, data = Default_df)

tally(group_by(Default_df,dft_cat,pred_outcome_model4))
```

ROC (Reciever Operating Characteristics) curve

```{r}

pred <- prediction(Default_df$pred_prob_model4,Default_df$dft) # create a prediction object in R
class(pred)

perf <- performance(pred, "tpr", "fpr") # tpr and fpr are true and false positive rates
plot(perf, colorize=T)
```

Area under curve of ROC curve

```{r}
auc.perf <-  performance(pred, measure = "auc")
auc.perf@y.values
```

Additional Reading:

You can refer this link to get more understanding about Sensitivity, Specificity and ROC curve:
https://www.medcalc.org/manual/roc-curves.php
